---
title: "Homework 2"
output:
  html_document
---

### Loading Libraries
```{r}
library(tidyverse)
```

### Formatting plots
```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 22,
  fig.asp = .8,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

sclae_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
```{r}
library(p8105.datasets)
data("instacart")
```

### Instacart Dataset Descriptions

* The Instacart dataset includes `r length(instacart)` variables: `r variable.names(instacart)`.
* The dataset has `r nrow(instacart)` rows and `r ncol(instacart)` columns.
* The range of days since the prior order is (`r range(instacart$days_since_prior_order)`).
* The median number of items added to cart order is (`r median(instacart$add_to_cart_order)`).
* The total number of times an item was reordered is `r sum(instacart$reordered)`.

### Aisles: Count and Most Ordered

```{r}
instacart %>% 
  summarize(
    distinct_aisles = n_distinct(aisle))  
```
* There are 134 different aisles. 

Instructions
* Make a plot that shows the number of items ordered in each aisle, Arrange aisles sensibly, and organize your plot so others can read it.
```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n)) %>% 
  filter(n > 10000) %>% 
  ggplot(aes(x = n, y = aisle)) +
  geom_point(aes(color = aisle)) +
  labs(
    title = "Number of Items Orders by Aisle")
    x = "Number of Items Sold",
    y = "Item"
  )

```
The aisles where the most items are ordered from are 83 for fresh vegetables, 24 for fresh fruits, and 123 for packages vegetables fruits. 



# Problem 2

# Problem 3

