---
title: "Homework 2"
output:
  html_document:
    theme: yeti
    highlight: haddock
---

### Loading Libraries
```{r}
library(tidyverse)
```

### Formatting plots
```{r}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 22,
  fig.asp = .8,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis")

sclae_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
```{r}
library(p8105.datasets)
data("instacart")
```

### Instacart Dataset Descriptions

* The Instacart dataset includes `r length(instacart)` variables: `r variable.names(instacart)`.
* The dataset has `r nrow(instacart)` rows and `r ncol(instacart)` columns.
* The range of days since the prior order is (`r range(instacart$days_since_prior_order)`).
* The median number of items added to cart order is (`r median(instacart$add_to_cart_order)`).
* The total number of times an item was reordered is `r sum(instacart$reordered)`.

### Aisles: Count and Most Ordered

```{r}
instacart %>% 
  summarize(
    distinct_aisles = n_distinct(aisle))  
```
* There are 134 different aisles. 

### Creating a plot 
```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>%
  mutate(
    aisle = factor(aisle),
    aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = n, y = aisle)) +
  geom_point() +
  labs(
    title = "Number of Items Orders by Aisle",
    x = "Number of Items Sold",
    y = "Item"
  )
```
* The aisles where the most items are ordered from are 83 for fresh vegetables, 24 for fresh fruits, and 123 for packages vegetables fruits. 

### Instacart: Cleaning and filter
```{r}
popular_items = instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank < 4)
```

### Instacart: Table
```{r}
knitr::kable(head(popular_items[, 1:4]), "simple")
```

### Icecream: Cleaning and filtering
```{r}
applies_icecream = instacart %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarize(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = order_dow,
    values_from = mean_hour
  )
```

### Icecream: Table
```{r}
knitr::kable(head(applies_icecream[, 1:8]), "simple")
```

# Problem 2
```{r}
library(p8105.datasets)
data("brfss_smart2010")
```

### Cleaning Data

```{r}
brfss_smart2010 = brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health") %>% 
  drop_na(response) %>%
  mutate(response = str_to_lower(response),
        response = factor(response))
```

### 2002 states with 7 or more locations

```{r}
states_2002 = brfss_smart2010 %>% 
  filter(year == 2002) %>%
  count(locationabbr) %>% 
  filter(n >= 7)
```

### 2010 states with 7 or more locations

```{r}
states_2010 = brfss_smart2010 %>% 
  filter(year == 2010) %>%
  count(locationabbr) %>% 
  filter(n >= 7)
```


### String plot of excellent responses
```{r}
excellent = brfss_smart2010 %>% 
  filter(response == "excellent") %>% 
  group_by(locationdesc) %>% 
  mutate(average_data_value = mean(data_value)) %>% 
  select(year, average_data_value, locationdesc, locationabbr) %>% 
  ggplot(aes(x = year, y = average_data_value, color = locationabbr)) +
  geom_point() + geom_line(aes(group = locationabbr))

excellent
```

### Distribution Plot
```{r}
plot_data = brfss_smart2010 %>% 
  filter(locationabbr == "NY") %>% 
  filter(year == c(2006,2010)) %>% 
  ggplot(aes(x = response, y = data_value, color = response)) + 
  geom_boxplot() + 
  facet_grid(. ~ year)

plot_data
```

# Problem 3

```{r}
accel = read_csv(file = "data/accel_data.csv")
```

### Accelerometer Dataset Cleaning 

```{r}
clean_accel = accel %>% 
  janitor::clean_names() %>% 
  mutate(week_day = ifelse(day %in% c("Saturday", "Sunday"), "weekday", "weekend")) %>% 
  select(week_day, everything()) %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "activity_day",
    values_to = "activity_counts")
```
 
    
### Accelerometer Dataset Description

* The Accelerometer dataset includes variables week_day, week, day_id, day, and activity.
* The dataset has `r nrow(accel)` rows and `r ncol(accel)` columns.
* The range of activity on day 1 is (`r range(accel$activity_1)`).
* The total amount of activity on day 1 is `r sum(accel$activity_1)`.

### Aggregating Accelerometer Dataset 

```{r}
clean_accel = clean_accel %>%
  group_by(day_id) %>% 
  summarize(sum_activity = sum(activity_counts)) 
```

```{r}
knitr::kable(head(clean_accel[, 1:2]), "simple")
```

